---
title: "Inference for numerical data"
author: "Thomas Willoughby"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(infer)
library(skimr)

set.seed(1234)
```

### Exercise 1

Each case represents one person, specifically, one high schooler

There are 13583 cases

```{r code-chunk-label}
nrow(yrbss)
```

### Exercise 2

```{r}
yrbss %>% 
  skim()
```

There are 1004 missing weights from the data set.

### Exercise 3

```{r}
yrbss <- yrbss %>% 
  mutate(physical_3plus = if_else(physically_active_7d > 2, "yes", "no"))

yrbss %>%
  filter(complete.cases(physical_3plus, weight)) %>%
  ggplot(aes(y = physical_3plus, x=weight)) +
  geom_violin()
```
There would seem to be a relationship between the two variables. It is not the relationship I would expect, It seems to show that high schoolers exercise 3 or more times a week have a higher mean eight than thoes who don't.

### Exercise 4

```{r}
yrbss %>%
  group_by(physical_3plus) %>%
  summarise(n = n())
```

Conditions: Independence and sample size

Both conditions are met as the data is taken by simple random sample, and it has a large sample size.



