---
title: "Inference for numerical data"
author: "Thomas Willoughby"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(infer)
library(skimr)

set.seed(1234)
```

### Exercise 1

Each case represents one person, specifically, one high schooler

There are 13583 cases

```{r code-chunk-label}
nrow(yrbss)
```

### Exercise 2

```{r}
yrbss %>% 
  skim()
```

There are 1004 missing weights from the data set.

### Exercise 3

```{r}
yrbss <- yrbss %>% 
  mutate(physical_3plus = if_else(physically_active_7d > 2, "yes", "no"))

yrbss %>%
  filter(complete.cases(physical_3plus, weight)) %>%
  ggplot(aes(y = physical_3plus, x=weight)) +
  geom_violin()
```
There would seem to be a relationship between the two variables. It is not the relationship I would expect, It seems to show that high schoolers exercise 3 or more times a week have a higher mean eight than thoes who don't.

### Exercise 4

```{r}
yrbss %>%
  group_by(physical_3plus) %>%
  summarise(n = n())
```

Conditions: Independence and sample size

Both conditions are met as the data is taken by simple random sample, and it has a large sample size.


### Exercise 5

Null Hypotheses: The mean weight is the same between the two groups, thoes who exercise 3+ times a week, and thoes who don't.
$$
H_{0} : \mu_{physical3+} = \mu_{physical3-}
$$
Alternative Hypotheses: The mean weight is different between the two groups.
$$
H_{1} : \mu_{physical3+} \neq \mu_{physical3-}
$$

### Exercise 6
```{r}
obs_diff <- yrbss %>%
  filter(complete.cases(weight, physical_3plus)) %>%
  specify(weight ~ physical_3plus) %>%
  calculate(stat = "diff in means", order = c("yes", "no"))


null_dist <- yrbss %>%
  filter(complete.cases(weight, physical_3plus)) %>%
  specify(weight ~ physical_3plus) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("yes", "no"))

ggplot(data = null_dist, aes(x = stat)) +
  geom_histogram() +
  geom_vline(xintercept = obs_diff$stat, color = "red")
```


### Exercise 7

```{r}
null_dist %>%
  filter(stat >= obs_diff$stat)
```

There are no permutations that have a difference at least as large or larger than obs_diff.

### Exercise 8

The error given is
```
Warning: Please be cautious in reporting a p-value of 0. This result is an approximation based on the number of `reps` chosen in the `generate()` step. See `get_p_value()`(`?infer::get_p_value()`) for more information."
```

There was 0 permutations that include that mean in the generated null distribution. This is not representative of the population.

```{r}
null_dist %>%
  get_p_value(obs_stat = obs_diff, direction = "two_sided")
```


### Exercise 9

```{r}
ci <- yrbss %>%
  filter(complete.cases(weight, physical_3plus)) %>%
  specify(weight ~ physical_3plus) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order=c("yes","no")) %>%
  get_ci(level = 0.95)
ci
```
We are 95% confident that the true difference between the weights of those who exercise at least three times a week and those who don’t lies between `r ci[1,1]` and `r ci[1,2]`

### Exercise 10

```{r}
ci_2 <- yrbss %>%
  filter(complete.cases(height)) %>%
  specify(response = height) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean") %>%
  get_ci(level = 0.95)
ci_2
```

We are 95% confident that the true difference between the weights of those who exercise at least three times a week and those who don’t lies between `r ci_2[1,1]` and `r ci_2[1,2]`


